Equalizer\\Programming and User Guide

### 2012-03-16 Developer/ProgrammingGuide/paper.tex
Post-release cleanup

\title{\vspace{7cm}
Equalizer 1.2\\Programming and User Guide}
\author{Eyescale Software GmbH}

%\date{
%  \vspace{14cm}
%  \begin{textblock}{}(0,4.5)
%    \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
%  \end{textblock}
%      {\Large The official reference for developing and
%        deploying parallel, scalable OpenGL\texttrademark\ applications using
%        the Equalizer parallel rendering framework}\\\vspace{1cm}
%      Version 1.10 for Equalizer 1.2\\[\medskipamount]
%  \today
%}

@@

\lstset{language=C++}
\section*{Equalizer 1.2 Programming and User Guide}
\today
\subsection*{Contributors}

@@

\begin{wrapfigure}{r}{.382\textwidth}
  \vspace{-2ex}\includegraphics[width=.382\textwidth]{images/eventFilter.pdf}
  {\caption{\label{fEventProcessing}Event Processing}}\vspace{-4ex}
\end{wrapfigure}
Events are received by an event handler. The event handler finds the
\textsf{eq::Sys\-tem\-Win\-dow} associated to the event. It then creates a
generic \textsf{Event}, which holds the event data in an independent format. The
original native event and this generic \textsf{Event} form the
\textsf{SystemWindowEvent}, which is passed to the concrete
\textsf{SystemWindow} for processing.

@@

%\cleardoublepage
%\pagestyle{empty}
%\begin{textblock}{}(0,4.5)
%  \hspace{-1cm}\includegraphics[width=22cm]{images/teaserBack.pdf}
%\end{textblock}

>>>>

\title{
Equalizer\\Programming and User Guide}
\author{Eyescale Software GmbH}

\date{
  \vspace{14cm}
  \begin{textblock}{}(0,4.5)
    \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{textblock}
      {\Large The official reference for developing and
        deploying parallel, scalable OpenGL\texttrademark\ applications using
        the Equalizer parallel rendering framework}\\\vspace{1cm}
      Version 1.10 for Equalizer 1.2\\[\medskipamount]
  \today
}

@@

\lstset{language=C++}
\section*{Equalizer Programming and User Guide}
\today
\subsection*{Contributors}

@@

\begin{wrapfigure}{r}{.382\textwidth}
  \vspace{-2ex}\includegraphics[width=.382\textwidth]{images/eventFilter.pdf}
  {\caption{\label{fEventProcessing}Event Processing}}
\end{wrapfigure}
Events are received by an event handler. The event handler finds the
\textsf{eq::Sys\-tem\-Win\-dow} associated to the event. It then creates a
generic \textsf{Event}, which holds the event data in an independent format. The
original native event and this generic \textsf{Event} form the
\textsf{SystemWindowEvent}, which is passed to the concrete
\textsf{SystemWindow} for processing.

@@

\cleardoublepage
\pagestyle{empty}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaserBack.pdf}
\end{textblock}
